### 2019-01-01 README.Rmd
spellcheck

@@

### Installing areal
The development version of `areal` can be accessed from Github with `remotes`:

>>>>

## Bug Fixes in v0.1.3
The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:

1. If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values. The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
2. Some intersections of `sf` geometries will result in geometry collections being created. This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed. The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`. The simplest workaround is to install the development version of `areal` from GitHub.

Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!

@@

### Installing areal
The easiest way to get `areal` is to install it from CRAN:

``` r
install.packages("areal")
```

The development version of `areal` can be accessed from GitHub with `remotes`:
